MSOA Industrial Electricty and Gas maps

### 2021-09-17 MSOA non domestic Elec and Gas.Rmd
Trying to sort the organisation of the knit file

# this will not print anything out when knitted due to the include=FALSE setting in the chunk header
message("User: ", user)
message("dataFolder: ", dataFolder)
```

# Mapping the Middle Layer Super Output Areas (MSOA)

```{r Loading in the Boundary Data for the MSOA}
inf <-paste0(dataFolder, "boundaries/MSOA/msoa_solent.shp")
message("Loading Middle Layer Super Output Area (MSOA) from file")
#When using shp files you might also need to have other supplementary files in the same folder to allow it to run https://cfss.uchicago.edu/notes/simple-features/
msoa_sf_data <- sf::read_sf(inf) 
head (msoa_sf_data)
table(msoa_sf_data$LAD11NM)#how many MSOAs are in each LA
```

## Mapping Commercial
### Mapping Electricty
####2019
```{r Loading in the MSOA electricity consumption data for industry }
# electricity consumption data for industry at MSOA level (pre downloaded)
inFile <-paste0(dataFolder, "energy/electricity/MSOA NonDom Elec csv/MSOA_NONDOM_2019.csv")
msoa_elecDatanondom <- readr::read_csv(inFile)
head(msoa_elecDatanondom)
```

```{r Mapping the electrcity consumption of the MSOAs Industrial Sector}
msoa_elecDatanondom$MSOA11CD <- msoa_elecDatanondom$ 'Middle Layer Super Output Area (MSOA) Code' 
msoa_merged_sf_nondom <-merge(msoa_sf_data, msoa_elecDatanondom)
ggplot2::ggplot(msoa_merged_sf_nondom) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Electricity: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Solent (all MSOAs)")
#mapping it
```
####Map Overlay
```{r Check leaflet for non dom elec consumption}
library (leaflet)

@@

```
####Difference from 2010 to 2019
```{r Creating the mean electricty consumption from the industrial sector MOSA}
ndelec_msoa_2010<-readr::read_csv(paste0(dataFolder,"energy/electricity/MSOA NonDom Elec csv/MSOA_NONDOM_2010.csv"))
ndelec_msoa_2019<-readr::read_csv(paste0(dataFolder,"/energy/electricity/MSOA NonDom Elec csv/MSOA_NONDOM_2019.csv"))
ndelec_msoa_2010$ndelec2010<-ndelec_msoa_2010$'Mean consumption (kWh per meter)'                                       
ndelec_msoa_2019$ndelec2019<-ndelec_msoa_2019$'Mean consumption (kWh per meter)'
merged_ndelec<-merge(ndelec_msoa_2010, ndelec_msoa_2019, by = "Middle Layer Super Output Area (MSOA) Code", all=TRUE)
names(merged_ndelec)
merged_ndelec$ndelec_diff<-(as.numeric(merged_ndelec$ndelec2019))-(as.numeric(merged_ndelec$ndelec2010))
summary(merged_ndelec)
```

@@

msoa_nd20102019$pc_diff <-100*(msoa_nd20102019$ndelec_diff/msoa_nd20102019$ndelec2010)
t_diff <- dplyr::select(as.data.frame(msoa_nd20102019),MSOA11CD, 'Middle Layer Super Output Area (MSOA) Code', ndelec2010, ndelec2019,ndelec_diff, pc_diff)
head(arrange(t_diff, pc_diff))
head(arrange(t_diff, -pc_diff))
ggplot2::ggplot(t_diff, aes(x=pc_diff)) +
  geom_histogram()
```
####Map with Overlay
```{r Check leaflet for change in non dom elec consumption}
library(leaflet)

@@

```{r Mapping the percentage change in mean electricty consumption from the industrial sector MOSA}
merged_ndelec$MSOA11CD<-merged_ndelec$"Middle Layer Super Output Area (MSOA) Code"
msoa_nd20102019<-merge(msoa_sf_data, merged_ndelec) #merging these
ggplot2::ggplot(msoa_nd20102019)+geom_sf(aes(fill=ndelec_diff/ndelec2010))+scale_fill_continuous(name="Change in electricty:Mean kWh per meter",low="green",high="red")+labs(caption ="Solent (all MSOAs)")##Why does this look like this? Increased efficiency? Businesses closing down?
```
#####Cities in more detail
```{r Southampton MSOA difference in non dom Elec}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(msoa_nd20102019, LAD11NM == "Southampton")
# plotting the electricity consumption of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = ndelec_diff/ndelec2010)) +
  scale_fill_continuous(name = "Change in Mean comsumpton (kWh per meter)", low = "green", high = "red") +
  labs(caption = "Southampton")
```
```{r Portsmouth LSOA difference in dom Elec}
#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
mapData <- dplyr::filter(msoa_nd20102019, LAD11NM == "Portsmouth")
# plotting the electricity consumption of Portsmouth in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = ndelec_diff/ndelec2010)) +
  scale_fill_continuous(name = "Change in Mean comsumpton (kWh per meter)", low = "green", high = "red") +
  labs(caption = "Portsmouth")
```
```{r Winchester LSOA difference in dom Elec}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(msoa_nd20102019, LAD11NM == "Winchester")
# plotting the electricity consumption of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = ndelec_diff/ndelec2010)) +
  scale_fill_continuous(name = "Change in Mean comsumpton (kWh per meter)", low = "green", high = "red") +
  labs(caption = "Winchester")
```
### Mapping Gas
####2019
```{r Loading in the MSOA gas consumption data for industry }
# gas consumption data for industry at MSOA level (pre downloaded)
inFile <-paste0(dataFolder, "energy/gas/MSOA NonDom Gas csv/MSOA_NonDom_Gas_2019.csv")
msoa_ndgas <- readr::read_csv(inFile)
head(msoa_ndgas)
```

@@

####Mapping the difference in non domestic gas from 2010 to 2019 
```{r Creating the difference in non domestic gas consumption in the MSOA}
msoa_2010_ndgas<-readr::read_csv(paste0(dataFolder,"/energy/gas/MSOA NonDom Gas csv/MSOA_NonDom_Gas_2010.csv"))
msoa_2019_ndgas<-readr::read_csv(paste0(dataFolder,"energy/gas/MSOA NonDom Gas csv/MSOA_NonDom_Gas_2019.csv"))
msoa_2010_ndgas$ndgas2010<-msoa_2010_ndgas$'Mean consumption (kWh per meter)'
msoa_2019_ndgas$ndgas2019<-msoa_2019_ndgas$'Mean consumption (kWh per meter)'

@@

```
####Map with Overlay
```{r Check leaflet for Change in non dom gas consumption}
library(leaflet)

>>>>

# this will not print anything out when knitted due to the include=FALSE setting in the chunk header
message("User: ", user)
message("dataFolder: ", dataFolder)
```
# Background Data
```{r Loading in the Boundary Data for the MSOA}
inf <-paste0(dataFolder, "boundaries/MSOA/msoa_solent.shp")
message("Loading Middle Layer Super Output Area (MSOA) from file")
#When using shp files you might also need to have other supplementary files in the same folder to allow it to run https://cfss.uchicago.edu/notes/simple-features/
msoa_sf_data <- sf::read_sf(inf) 
head (msoa_sf_data)
table(msoa_sf_data$LAD11NM)#how many MSOAs are in each LA
```
# Mapping Electricty
##2019
```{r Loading in the MSOA electricity consumption data for industry }
# electricity consumption data for industry at MSOA level (pre downloaded)
inFile <-paste0(dataFolder, "energy/electricity/MSOA NonDom Elec csv/MSOA_NONDOM_2019.csv")
msoa_elecDatanondom <- readr::read_csv(inFile)
head(msoa_elecDatanondom)
```

```{r Mapping the electrcity consumption of the MSOAs Industrial Sector}
msoa_elecDatanondom$MSOA11CD <- msoa_elecDatanondom$ 'Middle Layer Super Output Area (MSOA) Code' 
msoa_merged_sf_nondom <-merge(msoa_sf_data, msoa_elecDatanondom)
ggplot2::ggplot(msoa_merged_sf_nondom) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Electricity: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Solent (all MSOAs)")
#mapping it
mean(msoa_merged_sf_nondom$`Mean consumption (kWh per meter)`)
```
###Map Overlay
```{r Check leaflet for non dom elec consumption}
library (leaflet)

@@

```
##Difference from 2010 to 2019
```{r Creating the mean electricty consumption from the industrial sector MOSA}
ndelec_msoa_2010<-readr::read_csv(paste0(dataFolder,"energy/electricity/MSOA NonDom Elec csv/MSOA_NONDOM_2010.csv"))
ndelec_msoa_2019<-readr::read_csv(paste0(dataFolder,"/energy/electricity/MSOA NonDom Elec csv/MSOA_NONDOM_2019.csv"))
ndelec_msoa_2010$ndelec2010<-ndelec_msoa_2010$'Mean consumption (kWh per meter)'                                       
ndelec_msoa_2019$ndelec2019<-ndelec_msoa_2019$'Mean consumption (kWh per meter)'
merged_ndelec<-merge(ndelec_msoa_2010, ndelec_msoa_2019, by = "Middle Layer Super Output Area (MSOA) Code", all=TRUE)
names(merged_ndelec)
merged_ndelec$ndelec_diff<-(as.numeric(merged_ndelec$ndelec2019))-(as.numeric(merged_ndelec$ndelec2010))
summary(merged_ndelec)
```

@@

msoa_nd20102019$pc_diff <-100*(msoa_nd20102019$ndelec_diff/msoa_nd20102019$ndelec2010)
t_diff <- dplyr::select(as.data.frame(msoa_nd20102019),MSOA11CD, 'Middle Layer Super Output Area (MSOA) Code', ndelec2010, ndelec2019,ndelec_diff, pc_diff)
head(arrange(t_diff, pc_diff))
head(arrange(t_diff, -pc_diff))
ggplot2::ggplot(t_diff, aes(x=pc_diff)) +
  geom_histogram()
```
###Map with Overlay
```{r Check leaflet for change in non dom elec consumption}
library(leaflet)

@@

```
```{r Mapping the percentage change in mean electricty consumption from the industrial sector MOSA}
merged_ndelec$MSOA11CD<-merged_ndelec$"Middle Layer Super Output Area (MSOA) Code"
msoa_nd20102019<-merge(msoa_sf_data, merged_ndelec) #merging these
ggplot2::ggplot(msoa_nd20102019)+geom_sf(aes(fill=ndelec_diff/ndelec2010))+scale_fill_continuous(name="Change in electricty:Mean kWh per meter",low="green",high="red")+labs(caption ="Solent (all MSOAs)")##Why does this look like this? Increased efficiency? Businesses closing down?
```
###Cities in more detail
```{r Southampton MSOA difference in non dom Elec}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(msoa_nd20102019, LAD11NM == "Southampton")
# plotting the electricity consumption of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = ndelec_diff/ndelec2010)) +
  scale_fill_continuous(name = "Change in Mean comsumpton (kWh per meter)", low = "green", high = "red") +
  labs(caption = "Southampton")
```
```{r Portsmouth LSOA difference in dom Elec}
#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
mapData <- dplyr::filter(msoa_nd20102019, LAD11NM == "Portsmouth")
# plotting the electricity consumption of Portsmouth in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = ndelec_diff/ndelec2010)) +
  scale_fill_continuous(name = "Change in Mean comsumpton (kWh per meter)", low = "green", high = "red") +
  labs(caption = "Portsmouth")
```
```{r Winchester LSOA difference in dom Elec}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(msoa_nd20102019, LAD11NM == "Winchester")
# plotting the electricity consumption of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = ndelec_diff/ndelec2010)) +
  scale_fill_continuous(name = "Change in Mean comsumpton (kWh per meter)", low = "green", high = "red") +
  labs(caption = "Winchester")
```
# Mapping Gas
##2019
```{r Loading in the MSOA gas consumption data for industry }
# gas consumption data for industry at MSOA level (pre downloaded)
inFile <-paste0(dataFolder, "energy/gas/MSOA NonDom Gas csv/MSOA_NonDom_Gas_2019.csv")
msoa_ndgas <- readr::read_csv(inFile)
head(msoa_ndgas)
```

@@

##Mapping the difference in non domestic gas from 2010 to 2019 
```{r Creating the difference in non domestic gas consumption in the MSOA}
msoa_2010_ndgas<-readr::read_csv(paste0(dataFolder,"/energy/gas/MSOA NonDom Gas csv/MSOA_NonDom_Gas_2010.csv"))
msoa_2019_ndgas<-readr::read_csv(paste0(dataFolder,"energy/gas/MSOA NonDom Gas csv/MSOA_NonDom_Gas_2019.csv"))
msoa_2010_ndgas$ndgas2010<-msoa_2010_ndgas$'Mean consumption (kWh per meter)'
msoa_2019_ndgas$ndgas2019<-msoa_2019_ndgas$'Mean consumption (kWh per meter)'

@@

```
###Map with Overlay
```{r Check leaflet for Change in non dom gas consumption}
library(leaflet)
